GSE158433: GMEA of DNA methylation and RNA-seq differences in lung squamous cell carcinoma

### 2022-05-24 GSE158433/GSE158433_gmea.Rmd
integrative analysis begun

gmea_volc(res2)
gmea_barplot(res2)
res2_wg <- res2

@@

@@

metric <- res2$sig * res2$median
metric <- as.data.frame(metric)
rownames(metric) <- rownames(res2)

mres <- mitch_calc(x=metric, genesets=genesets)

@@

@@

gmea_volc(res2)
gmea_barplot(res2)
res2_p <- res2

@@

```{r,mitchpromoter}

@@

metric <- res2$sig * res2$median
metric <- as.data.frame(metric)
rownames(metric) <- rownames(res2)

mres <- mitch_calc(x=metric, genesets=genesets)

@@

## save data object

```{r,save}

save.image("GSE158422.Rdata")

@@

>>>>

gmea_volc(res2)
gmea_boxplot(res)
res2_wg <- res2

@@

Methylation only.

@@

meth <- res2$sig * res2$median
meth <- as.data.frame(meth)
rownames(meth) <- rownames(res2)

mres <- mitch_calc(x=meth, genesets=genesets)

@@

Methylation and gene expression.

```{r,integrate_wg}

dge <- read.table("GSE158420_dge.tsv")
dgem <- mitch_import(dge,DEtype="deseq2")

int <- merge(meth,dgem,by=0)
rownames(int) <- int$Row.names
int[,1]=NULL
names(int) <- c("meth","rna")

int_res <- mitch_calc(int,genesets=genesets)

int_res_tbl <- int_res$enrichment_result

head(int_res_tbl, 20) %>%
  kbl(caption = "Integrative results with mitch") %>%
  kable_paper("hover", full_width = F)

plot(int_res_tbl$s.meth,int_res_tbl$s.rna,ylab="RNA",xlab="meth")

abline(h=0,lty=2,lwd=2,col="red")
abline(v=0,lty=2,lwd=2,col="red")

uu <- length(which(int_res_tbl$s.meth>0 & int_res_tbl$s.rna>0))
ud <- length(which(int_res_tbl$s.meth>0 & int_res_tbl$s.rna<0))
dd <- length(which(int_res_tbl$s.meth<0 & int_res_tbl$s.rna<0))
du <- length(which(int_res_tbl$s.meth<0 & int_res_tbl$s.rna>0))

uu
ud
dd
du

uu + dd
ud + du

mitch_report(int_res,outfile="int_wholegene.html",overwrite=TRUE)

@@

gmea_volc(res2)
gmea_boxplot(res)
res2_p <- res2

@@

Methylation only

```{r,mitchpromoter1}

@@

pmeth <- res2$sig * res2$median
pmeth <- as.data.frame(pmeth)
rownames(pmeth) <- rownames(res2)

mres <- mitch_calc(x=pmeth, genesets=genesets)

@@

Methylation and gene expression.

```{r,integrate_promoter}

#dge <- read.table("GSE158420_dge.tsv")
#dgem <- mitch_import(dge,DEtype="deseq2")

int <- merge(pmeth,dgem,by=0)
rownames(int) <- int$Row.names
int[,1]=NULL
names(int) <- c("meth","rna")

int_res <- mitch_calc(int,genesets=genesets)
int_res_tbl <- int_res$enrichment_result

head(int_res_tbl,20) %>%
  kbl(caption = "Integrative results with mitch") %>%
  kable_paper("hover", full_width = F)

int_res_tbl <- int_res_tbl[order(-abs(int_res_tbl$s.dist)),]

head(int_res_tbl,20) %>%
  kbl(caption = "Integrative results with mitch") %>%
  kable_paper("hover", full_width = F)

plot(int_res_tbl$s.meth,int_res_tbl$s.rna,ylab="RNA",xlab="meth")

abline(h=0,lty=2,lwd=2,col="red")
abline(v=0,lty=2,lwd=2,col="red")

uu <- length(which(int_res_tbl$s.meth>0 & int_res_tbl$s.rna>0))
ud <- length(which(int_res_tbl$s.meth>0 & int_res_tbl$s.rna<0))
dd <- length(which(int_res_tbl$s.meth<0 & int_res_tbl$s.rna<0))
du <- length(which(int_res_tbl$s.meth<0 & int_res_tbl$s.rna>0))

uu
ud
dd
du

uu + dd
ud + du

mitch_report(int_res,outfile="int_promoter.html",overwrite=TRUE)

@@

## Session Information

```{r,session}

sessionInfo()
